---
title       : Motor Trend Car Road Tests
subtitle    : Coursera Developing Data Products Course Project
author      : Eric Koo
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Description

This course project uses data from the mtcars dataset from the R datasets library. It allows the user to interactively compare the relationship between two variables at a time by displaying a scatterplot, best-fit line, and resulting linear model.

- Link to Shiny App: https://ericiskoo.shinyapps.io/DevDataProd_Project1/
- Link to Shiny App GitHub Repository: https://github.com/ericiskoo/DevDataProd_Project1
- Link to Slides GitHub Repository: https://github.com/ericiskoo/DevDataProd_Project2

---

## Dataset

### Motor Trend Car Road Tests

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r}
library(datasets)
head(mtcars)
```

---

## Variables

For the purposes of this project, only the following 6 continuous variables can be compared and plotted:

- Miles/(US) gallon
- Displacement (cu.in.)
- Gross horsepower
- Rear axle ratio
- Weight (lb/1000)
- 1/4 mile time

---

## Example Plot

Miles/(US) gallon vs. Weight (lb/1000) 

```{r, echo=FALSE}
plot(mtcars$mpg, mtcars$wt)
abline(lm(mtcars$wt~mtcars$mpg), col="red")
```

